Liveness-Based Garbage Collection for Lazy Languages

### 2015-11-27 paper/paper.tex
Fig 1 (motiv example) fixed

%------------------------------------------------------------%
\subsection{Motivating Example}
\label{sec:motiv}
\begin{figure}[t!]
  \psset{unit=1mm}
  \begin{pspicture}(90,52)(0,-52)
    %\psframe(90,48)(0,-48)
    \renewcommand{\arraystretch}{1}
    \begin{tabular}{@{}c@{}}
      %\psframebox
          {\sf
	\renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
            \UFL\
            \UNL{0} (\DEFINE\ (\length\  \pl)
	    \UNL{1}  (\SIF~(\NULLQ \ \pl) $0$
            (\PRIM\ 1\ (\length\  (\CDR\  \pl)))))
            \UNL{0}
	    \UNL{0}  (\DEFINE\ (\append\  \lista\ \listb)
	    \UNL{1}  (\SIF~(\NULLQ \ \lista)
	    \listb
	    \UNL{2} \hspace*{-0.1cm}(\CONS\ (\CAR\ \lista) (\append\
            (\CDR\  \lista)
            \listb))))
            \UNL{0}
            \UNL{0} (\LET\ \px\
            $\leftarrow$\ (\CONS\ $5$
            (\CONS\ (\CONS\ $6$ \NIL) \NIL) \IN
	    \UNL{1} (\LET\ \py\   $\leftarrow$\  (\CONS\ $3$ \NIL) \IN
	    \UNL{2}
            (\LET\ \pz\  $\leftarrow$\  (\append\ \px\  \py)\ \IN\
            \UNL{3} (\SIF~(\NULLQ~(\CAR~\pz))~$0$~$\pi$:\
            (\length\ \pz))))))
	  \end{uprogram}
      }}
      \\ \\
      (a) Example program. \\  \\
%      \includegraphics[width=.45\textwidth]{motiv-example}
      \input{mem-graph} \\ \\
      \renewcommand{\arraystretch}{.9}
      \begin{tabular}[t]{p{0.9\columnwidth}}
        (b) Memory graph at $\pi$.  \scalebox{.7}{\TwoCellsAD{a1}{a2}}
        denotes a closure. Thick edges denote live links. Traversal
        stops at edges marked $\times$ during garbage collection for
        a liveness-based collector.
      \end{tabular}
    \end{tabular} 
  \end{pspicture}
%  \vspace*{-3ex}
  \caption{Example Program and its Memory Graph}\label{fig:mot-example}
\end{figure}

Figure~\ref{fig:mot-example} shows an example program and the state of
the heap at  the program point $\pi$, i.e. just  before the evaluation
of $(\length\  \pz)$.  The heap is  represented by a graph  in which a
node either  represents atomic  values ($\NIL$,  integers etc.),  or a
\CONS\  cell  containing  $\CAR$  and  $\CDR$  fields,  or  a  closure
(represented  by  shaded  clouds).   Edges   in  the  graph  are  {\em
  references} and represent  variables  or fields.  The figure shows
the  lists \px\  and  \pz\ partially  evaluated.   The evaluation  was
triggered by the test (\NULLQ~(\CAR~\pz)) in the \SIF\ expression.

@@

\newpage
\ 
\newpage

\section{Appendix: Soundness of liveness analysis}

>>>>

%------------------------------------------------------------%
\subsection{Motivating Example}
\label{sec:motiv}
\input{fig_motiv}
Figure~\ref{fig:mot-example} shows an example program and the state of
the heap at  the program point $\pi$, i.e. just  before the evaluation
of $(\length\  \pz)$.  The heap is  represented by a graph  in which a
node either  represents atomic  values ($\NIL$,  integers etc.),  or a
\CONS\  cell  containing  $\CAR$  and  $\CDR$  fields,  or  a  closure
(represented  by  shaded  clouds).   Edges   in  the  graph  are  {\em
  references} and represent  variables  or fields.  The figure shows
the  lists \px\  and  \pz\ partially  evaluated.   The evaluation  was
triggered by the test (\NULLQ~(\CAR~\pz)) in the \SIF\ expression.

@@

\clearpage
\section{Appendix: Soundness of liveness analysis}
